Using traffic analysis to identify The Second Generation Onion Router

### 2011-03-20 thesis/thesis.tex
Start of rewriting background

The Internet has revolutionised the political sphere in providing a platform
for the publication of speech to a far greater audience than was ever available
before digital communications systems \parencite{Bonchek:1997p3455}. The
publication of less desirable political speech, criticism or challenging ideas
still carries with it great risk, with numerous publications leading to arrest.
This has spawned headlines such as \textcite{website:egypt-arrests},
\citetitle{website:china-yahoo-torture}
\parencite{website:china-yahoo-torture},
\citetitle{website:vietnam-bloggers-arrested}
\parencite{website:vietnam-bloggers-arrested},
\textcite{website:iran-bloggers-arrested} and
\citetitle{website:blogger-arrests} \parencite{website:blogger-arrests}. The
Internet, like conventional media, is still vulnerable to censorship by
oppressive governments and malicious attackers
\parencite{Crandall:2007p6165,Karlin:2009p6166}.

In response to these threats, a number of systems have been proposed which use
various techniques, primarily cryptography and covering traffic, to provide
censorship resistance and anonymity. The Second Generation Onion Router (Tor),
is an anonymous network which uses a variant of Onion Routing, to provide low
latency anonymous communications to a wide variety of Internet communications
protocols \parencite{Dingledine:2004p314}. It also aims to provide resistance
against censorship based blocking attempts \parencite{Dingledine:2008p1542}.

Although Tor succeeds to a certain extent in these goals, it may be possible to
use traffic analysis techniques to automatically identify Tor connections and
target them for attacks. Since Tor relies on large numbers of users for the
protections it provides, attacks that affect the reliability of the network can
discourage participation, making it ineffective. This paper proposes a traffic
analysis methodology for identifying Tor traffic which may be used for such
attacks in the future.

@@

@@

\begin{enumerate*}
  \item Can the traffic be classified using automated matching techniques?
  \item Do these networks have characteristics that make them readily
    distinguishable using heuristics based matching?
  \item Do they have characteristics that make them distinguishable using a
    machine learning technique?
  \item How long does a user have to be
    connected to the network before a confident match can be made?
\end{enumerate*}

>>>>

The first anonymous digital network, commonly known as MixNet was proposed in
\textcite{Chaum:1981p296}. The foundation of MixNet was the use of an
intermediary which forwarded messages from clients without any identifying
details. Numerous proposals and implementations followed such as Freedom
\parencite{Goldberg:1999p2231} and aChord \parencite{Hazel:2002p6929}. The
Second Generation Onion Router (Tor), is an anonymous network which uses a
variant of Onion Routing, to provide low latency anonymous communications to a
wide variety of Internet communications protocols
\parencite{Dingledine:2004p314}. It also aims to provide resistance against
censorship based blocking attempts \parencite{Dingledine:2008p1542}.

Tor was originally developed by the U.S. Naval Research Lab in 1997
\parencite{Syverson:1997kz} for application by the U.S. Navy. It has since been
adopted by The Tor Project, Inc. and is made publicly available, finding usage
in journalism, law enforcement, activism and military applications
\parencite{The-Tor-Project-Inc.:2011uq}. Tor is one of the most successful and
widely deployed anonymous networks, with an average of two hundred thousand
active users as of March 2011 \parencite{The-Tor-Project-Inc.:2011fk}.

Although Tor succeeds to a certain extent in providing anonymity and censorship
resistance. Under controlled conditions it is possible to distinguish Tor
traffic from other forms of encrypted traffic using traffic analysis. This makes
it easy for Tor users to be isolated and targeted for attacks. Since Tor relies
on large numbers of users for the protections it provides, attacks that affect
the reliability of the network can discourage participation, making it
ineffective. This paper describes a simple traffic analysis technique which can
be used to distinguish Tor traffic from another form of commonly encrypted
traffic.

@@

 While it has been the subject of much
academic literature, the primary objective of researchers has historically been
the attempt to reveal participant identities \parencite[3]{Murdoch:2005p325}.

@@

\begin{enumerate*}
  \item Can the traffic be classified using automated matching techniques?
  \item Do these networks have characteristics that make them readily
    distinguishable using heuristics based matching?
  \item Do they have characteristics that make them distinguishable using a
    machine learning technique?
  %\item How long does a user have to be
  %  connected to the network before a confident match can be made?
\end{enumerate*}
